Methodology for Assessing the State of the Practice for Domain X

### 2020-09-21 StateOfPractice/Methodology/Methodology.tex
updated section 7 link of Methodology doc
updated section 8 of Methodology doc

Note the following formatting conventions of this document. Red text denotes a link to information within the document. Purple text denotes a link to supplementary information that is external to this document.\pmi{needs to be added to intro to explain convention}

@@

A sample commonality analysis for Lattice Boltzmann Solvers can be found
\href{run:../Peter-Notes/Commonality-Analysis-LB-Systems.pdf}{here}.

\section{Empirical Measures} \label{SecEmpiricalMeasures}

\subsection{Raw Data}
The following raw data measures are extracted from repositories:

\begin{itemize}
\item Number of stars.
\item Number of forks.
\item Number of people watching the repository.
\item Number of open pull requests.
\item Number of closed pull requests.	
\item Number of developers.	
\item Number of open issues.
\item Number of closed issues.
\item Initial release date.
\item Last commit date.
\item Programming languages used.
\item Number of text-based files.
\item Number of total lines in text-based files.
\item Number of code lines in text-based files.
\item Number of comment lines in text-based files.
\item Number of blank lines in text-based files.
\item Number of binary files.  
\item Number of total lines added to text-based files.
\item Number of total lines deleted from text-based files.
\item Number of total commits.
\item Numbers of commits by year in the last 5 years. (Count from as early as possible if the project is younger than 5 years.) 
\item Numbers of commits by month in the last 12 months.
\end{itemize}

@@

\begin{itemize}
\item Status of software package (dead or alive).
\item Percentage of identified issues that are closed.
\item Percentage of code that is comments.
\end{itemize}

\subsection{Tool Tests}
The following tools are used to gather some of the raw data from the repositories:

\subsubsection{git-stats}\label{gitstats}
\href{https://github.com/tomgi/git_stats}{GitHub repo}

\subsubsection{scc}\label{scc}
\href{https://github.com/boyter/scc}{GitHub repo}

>>>>

Note the following formatting conventions of this document. Red text denotes a link to information within the document. Purple text denotes a link to supplementary information that is external to this document. Blue text denotes a URL link.\pmi{needs to be added to intro to explain convention}

@@

A sample commonality analysis for Lattice Boltzmann Solvers can be found
\href{https://github.com/smiths/AIMSS/blob/master/StateOfPractice/Peter-Notes/Commonality-Analysis-LB-Systems.pdf}{here}.

\section{Empirical Measures} \label{SecEmpiricalMeasures}
\pmi{Add introduction.  We should orient the reader on the purpose of this section, and provide a brief roadmap of the subsections.}

\subsection{Raw Data}
The following raw data measures are extracted from repositories:
\pmi{SS:"we should say why we are collecting this data. It is okay to say that we are collecting data that is reasonably easy to collect. We will then put the data together and analyze it. However, we should also relate the measures we are collecting to questions we want to answer. Ideally, we will relate the data to our research questions. For instance, we are collecting some of the data to see how large a project is. More files, more lines of code, etc, means a larger project. The number of developers is another measure of size. Other measures are intended to ascertain a project's popularity, like the number of stars and forks. Other measures are intended to see how active the project is, like the measures related to the history of commits."}
\begin{itemize}
\item Number of stars.
\item Number of forks.
\item Number of people watching the repository.
\item Number of open pull requests.
\item Number of closed pull requests.	
\item Number of developers.	
\item Number of open issues.
\item Number of closed issues.
\item Initial release date.
\item Last commit date.
\item Programming languages used.
\item Number of text-based files.
\item Number of total lines in text-based files.
\item Number of code lines in text-based files.
\item Number of comment lines in text-based files.
\item Number of blank lines in text-based files.
\item Number of binary files.  
\item Number of total lines added to text-based files.
\item Number of total lines deleted from text-based files.
\item Number of total commits.
\item Numbers of commits by year in the last 5 years. (Count from as early as possible if the project is younger than 5 years.) 
\item Numbers of commits by month in the last 12 months.
\end{itemize}

@@

\begin{itemize}
\item Status of software package (dead or alive). Alive is defined as the presence of repository commits or software package version releases in the last 18 months.
\item Percentage of identified issues that are closed.
\item Percentage of code that is comments.
\end{itemize}

\subsection{Tools}
\href{https://github.com/tomgi/git_stats}{GitStats} is used to measure the number of binary files as well as the number of added and deleted lines in a repository. The tool is also used to measuring the number of commits over different intervals of time. \href{https://github.com/boyter/scc}{Sloc Cloc and Code (scc)} is used to measure the number of text based files as well as the number of total, code, comment, and blank lines in a repository. These tools were selected due to their installability, usability, and ability to gather the above empirical measures. A guide for installing and running them can be found \href{run:A Guide to Empirical Measures.pdf}{here}.
